Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-06-12 revisionMemo/rev1.tex
formatting

		\item  \emph{ \textcolor{blue}{

@@

		%\item \textcolor{blue}{ \emph{
		%Aronow et al. also explicitly note that their approach does not deal with issues of third order dependence.
		%}}
		%\item \textcolor{blue}{ \emph{
		%Aronow et al. approach does not deal with bias in parameter estimates.
		%}}

@@

		\item {\emph{\textcolor{blue}{

@@

		}}}

@@

		\item \textcolor{blue}{ \emph{ We think the reviewer makes a good suggestion here to clarify, mathematically or in some other illustrative way, exactly how we think that dependencies bias the estimator. For example we can say that our target of inference is the estimation of beta (with some variance). If a coefficient is correlated with a dependency, then we could obtain an estimate for beta that is artificially high (and the same is true for the reverse).

@@

		\item  \emph{\textcolor{blue}{

@@

		\item \emph{\textcolor{blue}{Finally, we understand these goals are not always central to political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in Gleditsch and Ward 2013; Grimmer 2015; Neunhoeffer and Sternberg 2019; Colaresi and Mahmood 2017; and Mueller and Rauh 2018 among others.}

>>>>

@@

@@

@@

@@

		We think the reviewer makes a good suggestion here to clarify, mathematically or in some other illustrative way, exactly how we think that dependencies bias the estimator. For example we can say that our target of inference is the estimation of beta (with some variance). If a coefficient is correlated with a dependency, then we could obtain an estimate for beta that is artificially high (and the same is true for the reverse).

@@

@@

			Finally, we understand these goals are not always central to political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in Gleditsch and Ward 2013; Grimmer 2015; Neunhoeffer and Sternberg 2019; Colaresi and Mahmood 2017; and Mueller and Rauh 2018 among others.}
